### 2023-03-08 manuscript.tex
Changing pip git+ to f62dd4cfdebf67f99f63c9b2e64edeaa591eeb69 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/077b97a7cbbaa6291b5ae7dd0da4f671c4978aee.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/077b97a7cbbaa6291b5ae7dd0da4f671c4978aee/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4366864034

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/cd23484da8a997acd9bf63c08b6317c3d9e4ac2b/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/cd23484da8a997acd9bf63c08b6317c3d9e4ac2b}{SORTEE-Github-Hackathon/manuscript@cd23484}
on March 8, 2023.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/077b97a7cbbaa6291b5ae7dd0da4f671c4978aee/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/077b97a7cbbaa6291b5ae7dd0da4f671c4978aee}{SORTEE-Github-Hackathon/manuscript@077b97a}
on March 8, 2023.
